Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-25 journal/article.tex
S: People factors

Choosing people with a disposition towards agile methods was seen as a
requirement for the change to take the right track. Teams are staffed usually
based on technical competences, but considering personality aspects alike was
emphasized for agile teams [P29, P34]. The personality of people was seen as a
key aspect for achieving change [P6]. There was a need for collaborative and
understanding persons who are prepared to discard preconceptions and willing to
try new untested approaches [P6, P29].
% Also, having previous agile experience did not directly imply suitability to
% work in a larga scale agile environment [P34].
% In the beginning of the transformation team members who did not find themselves
% comfortable with the new model were exchanged for better suited persons [P29].

>>>>

Choosing people with a disposition towards agile methods was seen as a
requirement for the change to take the right track. Teams are staffed usually
based on technical competences, but considering personality aspects alike was
emphasized for agile teams [P29, P34]. The personality of people was seen as a
key aspect for achieving change [P6]. There was a need for collaborative and
understanding persons who are prepared to discard preconceptions and willing to
try new untested approaches [P6, P29].
% Also, having previous agile experience did not directly imply suitability to
% work in a large scale agile environment [P34].
% In the beginning of the transformation team members who did not find themselves
% comfortable with the new model were exchanged for better suited persons [P29].

% People with previous agile expertise

A few cases mentioned the importance people with previous agile experience had
at the start of the transformation [P6]. For instance, it helped the product
management office to implement agile over the entire enterprise when the
staffing of was updated to include people with agile experience [P10]. Staffing
teams partially with developers familiar with agile helped the rest of the team
get a good hold of agile development [P37].

% People without baggage of the past

A few cases discussed the benefit of having change leaders without baggage of
the past. Cowan [P11] describes how the newly hired director was able to
circumvent territorial battles that existed from before, and therefore focus
fully on getting the agile model implemented. In another case external coaches
were described to better spot places for correctino in the agile model, and
their advice was received better because they were considered impartial when
being external to the organization [P16].
% Old employees were also willing to try something new, because the organization
% had gone through a time of uncertainty and restructuring [P11].
